\sys: Automated Data-Parallel Shell Processing

### 2020-05-03 pldi/draft.tex
Plot for comparison with sort --parallel

>>>>

\kk{We have to remember to say that for this to work, all nodes in the
  graph must always open their outputs! If not, then this technique
  doesn't work, and we have to monitor if any node dies to do
  something with it. At the moment we ensure that by doing that in our
  nodes, and by assuming that all nodes that we handle do that.}
